---
title: "Nominal house prices data in Luxembourg"
author: "Bruno Rodrigues"
date: today
---

## Downloading the data

This data is downloaded from the "Observatoire de l'habitat":

```{r development, include=FALSE}
library(dplyr)
library(ggplot2)
library(janitor)
library(purrr)
library(readxl)
library(rvest)
library(stringr)
library(testthat)
```

```{r function-get_raw_data}

get_raw_data <- function(url = "https://data.public.lu/fr/datasets/r/1d20f982-57e1-4ae2-a278-dc78c88c21dc"){
  raw_data <- tempfile(fileext = ".xlsx")

  download.file(url, raw_data)

  sheets <- excel_sheets(raw_data)

  read_clean <- function(..., sheet){
    read_excel(..., sheet = sheet) %>%
      mutate(year = sheet)
  }

  raw_data <- map_dfr(sheets,
                      ~read_clean(raw_data,
                                  skip = 10,
                                  sheet = .)) %>%
    clean_names()

  raw_data %>%
    rename(locality = commune,
           n_offers = nombre_doffres,
           average_price_nominal_euros = prix_moyen_annonce_en_courant,
           average_price_m2_nominal_euros = prix_moyen_annonce_au_m2_en_courant,
           average_price_m2_nominal_euros = prix_moyen_annonce_au_m2_en_courant
           ) %>%
    mutate(locality = str_trim(locality)) %>%
    select(year, locality, n_offers, starts_with("average"))

}

```

```{r}
flat_data <- get_raw_data(url = "https://data.public.lu/fr/datasets/r/1d20f982-57e1-4ae2-a278-dc78c88c21dc")
```

Luxembourg is Luxembourg-ville in 2010 and 2011, then Luxembourg. Pétange is also spelled in two
ways also, converts make columns the right type. We also directly remove rows where the locality
contains information on the "Source". In the first version of the document this was done later
as we didn't know these rows where in there:

```{r function-clean_raw_data}
clean_raw_data <- function(raw_data){
  flat_data %>%
    mutate(locality = ifelse(grepl("Luxembourg-Ville", locality),
                             "Luxembourg",
                             locality),
           locality = ifelse(grepl("P.tange", locality),
                             "Pétange",
                             locality)
           ) %>%
    filter(!grepl("Source", locality)) %>%
    mutate(across(starts_with("average"), as.numeric))
}
```

```{r}
flat_data <- clean_raw_data(raw_data)
```

We now need to make sure that we got all the communes/localities in there. There were mergers in
2011, 2015 and 2018. So we need to account for these localities.

We’re now scraping data from wikipedia of former Luxembourguish communes:

```{r function-get_former_communes}

get_former_communes <- function(url = "https://en.wikipedia.org/wiki/Communes_of_Luxembourg#Former_communes",
                                min_year = 2009,
                                table_position = 3)

  read_html(url) %>%
    html_table() %>%
    pluck(table_position) %>%
    clean_names() %>%
    filter(year_dissolved > min_year)

```

```{r}
former_communes <- get_former_communes()
```

We can scrape current communes:

```{r function-get_current_communes}

get_current_communes <- function(url = "https://en.wikipedia.org/wiki/List_of_communes_of_Luxembourg",
                                 table_position = 1){
  read_html(url) %>%
    html_table() %>%
    pluck(table_position) %>%
    clean_names()
}

```

```{r}
current_communes <- get_current_communes()
```

Let’s now create a list of all communes:

```{r function-get_test_communes}

get_test_communes <- function(former_communes, current_communes){

  communes <- unique(c(former_communes$name, current_communes$commune))
  # we need to rename some communes

  # Different spelling of these communes between wikipedia and the data

  communes[which(communes == "Clemency")] <- "Clémency"
  communes[which(communes == "Redange")] <- "Redange-sur-Attert"
  communes[which(communes == "Erpeldange-sur-Sûre")] <- "Erpeldange"
  communes[which(communes == "Luxembourg-City")] <- "Luxembourg"
  communes[which(communes == "Käerjeng")] <- "Kaerjeng"
  communes[which(communes == "Petange")] <- "Pétange"

  communes
}

```

```{r}
communes <- get_test_communes(former_communes, current_communes)
```

We now need to check if we have them all in the data:

```{r tests-clean_flat_data}
testthat::expect_true(
            all(communes %in% unique(flat_data$locality))
                      )
```

Let’s keep the national average in another dataset:

```{r function-make_country_level_data}
make_country_level_data <- function(flat_data){
  country_level <- flat_data %>%
    filter(grepl("nationale", locality)) %>%
    select(-n_offers)

  offers_country <- flat_data %>%
    filter(grepl("Total d.offres", locality)) %>%
    select(year, n_offers)

  full_join(country_level, offers_country) %>%
    select(year, locality, n_offers, everything()) %>%
    mutate(locality = "Grand-Duchy of Luxembourg")

}

```

```{r}
country_level_data <- make_country_level_data(flat_data)
```

We can finish cleaning the commune data:

```{r function-make_commune_level_data}
make_commune_level_data <- function(flat_data){
  flat_data %>%
    filter(!grepl("nationale|offres", locality),
           !is.na(locality))
}

```

```{r}
commune_level_data <- make_commune_level_data(flat_data)
```

Let’s plot some data for good measure:

```{r}

commune_level_data %>%
  filter(locality %in% c("Luxembourg",
                         "Esch-sur-Alzette",
                         "Diekirch")) %>%
  ggplot() +
  geom_line(aes(y = average_price_m2_nominal_euros,
                x = year,
                group = locality,
                colour = locality))


country_level_data %>%
  ggplot() +
  geom_line(aes(y = average_price_m2_nominal_euros,
                x = year,
                group = locality,
                colour = locality))

```
